Relaxed Weak Accelerated Proximal Gradient Method: a Unified Framework for Nesterov's Accelerations

### 2025-10-07 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
>w<, changes

        \begin{lemma}[the consequencse of optimal momentum sequence]\;\label{lemma:opt-mmntm-seq}\\

@@

@@

            Combining \eqref{eqn:opt-mmntm-seq-pitem1}, \eqref{eqn:opt-mmntm-seq-pitem2} it would mean for all $i \ge 1$ it has: 

@@

            Since $\beta_i$ is monotone decreasing, it has $\beta_i^{-1/2}\beta_{i - 1}^{-1/2} \le 1$, and since $\alpha \in (0, 1)$
            \todoinline{HERE! IT'S NOT FINISHED YET!!!}

@@

            Let $(f, g, L)$, $(\alpha_k, B_k, \rho_k, \epsilon_k)_{k \ge 0}$, $(\beta_k)_{k\ge 0}, \mathcal E_0, p$ as assumed in Assumption \ref{ass:valid-err-schedule}. 

@@

                \item the sequence $(\alpha_k)_{k\ge 0}$ satisfies for all $k \ge 0$ the equality $(1 - \alpha_k) = \alpha_{k}^2L_k\alpha_{k - 1}^{-2}L_{k - 1}^{-1}$;

@@

                % \item the sequence $\rho_k$ must also recursively satisfies $\rho_k \ge \max\left(-B_k + \alpha_{k - 1}^4(\rho_{k - 1} + B_{k - 1}), 0\right)$. 

@@

            Telescope for all $i \ge 1$: 
                \frac{\alpha_0\sqrt{L_0}}{2}\sum_{i = 1}^{k}\sqrt{L^{-1}_k}
                \beta_k^{-1/2} - \beta_{0}^{-1/2} = 
                \beta_k^{-1/2} - 1. 
            Re-arranging, yields: 

@@

            Recall that $L_k = B_k + \rho_k$, and by our assumptions, the sequence $(B_k)_{k \ge 0}, (\rho_k)_{k\ge 0}$ are both bounded above, then it's not hard to see that $\beta_k \le \mathcal O(1/k^2)$. 
            Combine it with Lemma \ref{lemma:inxt-apg-cnvg-prep1}, using $\alpha_0 = 1$ will yield the desired result. 
            Finally, one can solve for $\alpha_k$ by the recursive equality, and it should always have one of the strictly positive root: 
                &\underset{(1)}{\le} \frac{\alpha_{k - 1}^2L_{k - 1}}{2L_k}\left(
            At (1) we completed a square inside of the radical: 
                &\le (1 + 2L_kL_{k - 1}^{-1}\alpha_{k - 1}^{-2})^2. 
            To see that $\alpha_k > 0$, recall that we had the assumption that $B_k > 0$ making $L_k > 0$. 
            If we inductively assume that $\alpha_{k - 1} \in (0, 1]$ then $\alpha_k > 0$ because: 

@@

            The the next subsection, we will show that under the assumption of the above theorem, there exists an error sequence $\epsilon_k$ such that it can never approach $0$ at an arbitrarily fast rate. 

@@

>>>>

        \begin{lemma}[the properties of optimal momentum sequence]\;\label{lemma:opt-mmntm-seq}\\

@@

            Firstly, we will show that for all $\alpha_0 \in (0, 1]$, and $\alpha_k \in (0, 1)\;\forall k \ge 1$. 
            We prove using induction, inductively assume that $\alpha_k \in (0, 1]$. 
            We can solve for $\alpha_k$ using the recursive equality which should always have one of the strictly positive root given by: 
                &\underset{(1)}{<} \frac{\alpha_{k - 1}^2L_{k - 1}}{2L_k}\left(
            At (1) we completed a square inside of the radical, and use the assumption that $\alpha_k > 0$ and, $L_k > 0, L_{k - 1} > 0$ because we had $B_k > 0$: 
                &< \left(1 + 2L_kL_{k - 1}^{-1}\alpha_{k - 1}^{-2}\right)^2. 
            To see that $\alpha_k > 0$, recall the same fact that $L_k > 0$, and use the inductive hypothesis that $\alpha_{k - 1} \in (0, 1]$ then $\alpha_k > 0$ because: 
            Therefore, inductively it holds that $\alpha_k \in (0, 1)$ too. 

@@

            Combining \eqref{eqn:opt-mmntm-seq-pitem1}, \eqref{eqn:opt-mmntm-seq-pitem2} and the fact that $\beta_k > 0\;\forall k \ge 0$, it would mean for all $i \ge 1$ it has: 

@@

            Since $\beta_i$ is monotone decreasing, it has $0 < \beta_i^{-1/2}\beta_{i - 1}^{-1/2} \le 1$, this gives: 
                &\le \alpha_0\sqrt{\frac{L_0}{L_i}} 
                \le 2 \left(
            Performing a telescoping sum, use the fact that $\beta_0 = 1$ will yield the desired results after some algebraic manipulations. 

@@

            Let $(f, g, L)$, $(\alpha_k, B_k, \rho_k, \epsilon_k)_{k \ge 0}$, $(\beta_k)_{k\ge 0}, \mathcal E_0, p$ be given by Assumption \ref{ass:opt-mmntm-seq}. 

@@

@@

@@

            We use the results from \ref{lemma:opt-mmntm-seq} because the sequence has the same assumption, then using the fact that $L_k$ is bounded then it gives:

@@

            Then, apply Theorem \ref{prop:inxt-apg-cnvg-generic} to obtain the desired results.

@@

            In the next subsection, we will show that under the assumption of the above theorem, there exists an error sequence $\epsilon_k$ such that it can never approach $0$ at an arbitrarily fast rate. 

@@

        \begin{lemma}[error schedule lower bound]

### 2025-10-07 Notebook LaTEX/R-WAPG/presentation-shorter.tex
>w<, changes

\title{
    Relaxed Weak Accelerated Proximal Gradient Method: a Unified Framework for Nesterov's Accelerations
}
% \newcommand{\email}{lalala@lala.la}
\institute[UBCO]{
    University of British Columbia Okanagan
    \\
    WCOM 2025
}
\date[\today]{
    \today \\ \vspace{1cm} 
    \tiny{Joint work with Shawn/Xianfu Wang}\\ 
    \tiny{The research of HL and XW was partially supported by the NSERC Discovery Grant of Canada.}
    \tiny{We respectfully acknowledge that the UBC Okanagan academic campus is situated on the traditional, ancestral, unceded territory of the Syilx Okanagan Nation}
}

@@

\section{References and draft on arxiv}
    \begin{frame}{Thanks for the participations. Merci pour les participations.}
        Our paper can be found on arxiv using the following QR code: 
        \begin{figure}
            \centering
            \includegraphics[width=15em]{assets/paper-qrcode.png}
        \end{figure}
        Questions?
    \end{frame}
    \begin{frame}{References}        
        \bibliography{references/R-WAPG.bib}
    \end{frame}

>>>>

\title{
    Relaxed Weak Accelerated Proximal Gradient Method: a Unified Framework for Nesterov's Accelerations
}
% \newcommand{\email}{lalala@lala.la}
\institute[UBCO]{
    University of British Columbia Okanagan
    \\
    WCOM 2025
}
\date[\today]{
    \today \\ \vspace{1cm} 
    \tiny{Joint work with Shawn/Xianfu Wang}\\ 
}

@@

\section{References, acknowledgement and our draft on arxiv}
    \begin{frame}{Acknowledgements}
        \begin{tcolorbox}
            The research of HL and XW was partially supported by the NSERC Discovery Grant of Canada.
            \par
            We respectfully acknowledge that the UBC Okanagan academic campus is situated on the traditional, ancestral, unceded territory of the Syilx Okanagan Nation    
        \end{tcolorbox}
    \end{frame}
    \begin{frame}{Thanks for the participation. Merci pour les participations.}
        Our paper can be found on arxiv using the following QR code: 
        \begin{figure}
            \centering
            \includegraphics[width=15em]{assets/paper-qrcode.png}
        \end{figure}
        Questions?
    \end{frame}
    \begin{frame}{References}        
        \bibliography{references/R-WAPG.bib}
    \end{frame}
